---
title: "Fitting Generalized Linear Models"
author: "Jie Xue"
date: "June 20, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
```

## Case Study: Prediction of Body Fat
```{r, warning=FALSE, message=FALSE}
library("mboost")  ## load package
data("bodyfat", package = "TH.data")    ## load data
head(bodyfat)
```

The response variable is the body fat measured by DXA (DEXfat).

#### 1.A Reproduce formula of Garcia et al., 2005
```{r, 001}
lm1 <- lm(DEXfat ~ hipcirc + kneebreadth + anthro3a, data = bodyfat)
coef(lm1)
```


#### 1.B Estimate same model by glmboost
```{r, 002}
glm1 <- glmboost(DEXfat ~ hipcirc + kneebreadth + anthro3a, data = bodyfat)
coef(glm1, off2int=TRUE) ## off2int adds the offset to the intercept
```

Note that in this case we used the default settings in control and the default family Gaussian() leading to
boosting with the $L_2$ loss

### We now want consider all available variables as potential predictors.
#### 2.1 Build formula
```{r, 003}
preds <- names(bodyfat[, names(bodyfat) != "DEXfat"]) ## names of predictors
fm <- as.formula(paste("DEXfat ~", paste(preds, collapse = "+"))) ## build formula
fm
```

#### 2.2 Build model in 2 ways (identical results)
```{r, 004}
glm2a <- glmboost(fm, data = bodyfat)
glm2b <- glmboost(DEXfat ~ ., data = bodyfat)
identical(coef(glm2a), coef(glm2b))
```


### 3. A plot of the coefficient paths
#### 3.1 All coefficients
```{r, 005}
op <- par(mar = c(5,4,4,5.8) + 0.1)
plot(glm2b, off2int = TRUE) ## default plot, offset added to intercept
par(op)
```



#### 3.2 Change ylim to the range of the coefficients without intercept (zoom-in)
```{r, 006}
op <- par(mar = c(5,4,4,5.8) + 0.1)
plot(glm2b, ylim = range(coef(glm2b, which = preds)))
par(op)
```



